A Bradley-Terry analysis of three grandmasters: Karpov, Kasparov, Anand

### 2024-04-19 inst/kka.Rmd
typo

With strictly positive $D,D_1,D_2$ these are equal if and only if
$(\lambda-1)(p_1-p_2)=0$, that is, if the white advantage is
nonexistant, or if the players have the same strength.

>>>>

With strictly positive $D,D_1,D_2$ these are equal if and only if
$(\lambda-1)(p_1-p_2)=0$, that is, if the white advantage is
nonexistent, or if the players have the same strength.
